---
title: "Mapping the incidence rate of typhoid fever in sub-Saharan Africa"
output: github_document
date: "2023-02-10"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# devtools::install()
# library(TyphoidMapping)
# devtools::install_github("kimfinale/TyphoidMapping")
devtools::load_all()
```

####
Running the scripts below saves csv files in the output directory.

### Log-linear regression

```{r log-linear, eval=FALSE}
library(GGally)
res <- loglinear_model()
```


### Poisson regression

```{r poisson, eval=FALSE}
res <- poisson_model()
```

### Negative binomial regression

```{r negbin, eval=FALSE}
res1 <- negbin_model_1()
res2 <- negbin_model_2()
```


### Prepare covariates for prediction

I may change this code simply to raster::resample
```{r covprep, eval=FALSE}
pred_loc <- get_prediction_location()
pred_cov <- get_prediction_covariate()
```

### Forecasting for the log-linear model
```{r predict_loglinear, eval=FALSE}
pred <- predict_loglinear_model()
```

### Forecasting for the poissonl model
```{r predict_poisson, eval=FALSE}
pred <- predict_poisson_model()
```


### Forecasting for the NegBin 
```{r predict_negbin, eval=FALSE}
pred1 <- predict_negbin_model_1()
pred2 <- predict_negbin_model_2()
```


### Plots

#### Figure 1
```{r}

```

#### Figure 2
```{r}

```

#### Figure 3
```{r}

```

#### Figure 4
```{r}

```





